Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s08_pinnedline.tex
Minor modification in pinned line-incidence

A {\em pinned line-incidence system} $(G,\delta)$  
is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$, 
such that each edge is constrained to lie on a line passing through 
the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$  
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$  \cite{xxx}. Note that no trivial motion exists since the pins have fixed positions on the plane.
In particular, both a single vertex and a single edge are under-constrained graphs, 
and the smallest over-constrained graph has $6$ vertices.

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs, 
{\em a well-constrained pinned line-incidence graph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs. 
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. 
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We make the following corresponding modification to the definition of the DR-plan:

@@

 The {\em DR-plan} of  a well-constrained pinned line-incidence graph $G$ is one in which 
 each child node of a non-leaf node $C$ is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
 % Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}
\end{definition}

>>>>

A {\em pinned line-incidence system} $(G,\delta)$  
is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$, 
such that each edge is constrained to lie on a line passing through 
the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$  
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$  \cite{xxx}. Note that no trivial motion exists since the pins have fixed positions on the plane.
In particular, both a single vertex and a single edge are under-constrained graphs.
%and the smallest over-constrained graph has $6$ vertices.

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs, 
{\em a well-constrained pinned line-incidence graph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs. 
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. 
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We define a {\em trivial} graph to be a single vertex and make the following modification to the definition of the DR-plan:

@@

 The {\em DR-plan} of  a well-constrained pinned line-incidence graph $G$ is one in which 
(1) each child node of a non-leaf node $C$ is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$, and
(2) a leaf node is a single edge.
 % Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}
\end{definition}
